
\begin{thebibliography}{00}

% First citation: b20 (dataset) - appears in introduction
\bibitem{b1} M. Ahishali, ``Aerial Imagery for Standing Dead Tree Segmentation,'' Kaggle Datasets, 2025. [Online]. Available: \url{https://www.kaggle.com/datasets/meteahishali/aerial-imagery-for-standing-dead-tree-segmentation}. Accessed: Aug. 9, 2025.

% Second citation: b29 (Stereńczak 2017) - appears in literature review
\bibitem{b2} K. Stereńczak, B. Kraszewski, M. Mielcarek, and Ż. Piasecka, ``Inventory of standing dead trees in the surroundings of communication routes -- The contribution of remote sensing to potential risk assessments,'' \textit{Forest Ecology and Management}, vol. 402, pp. 76--91, 2017.

% Third citation: b25 (Cheng 2024) - appears in literature review  
\bibitem{b3} Y. Cheng et al., ``Scattered tree death contributes to substantial forest loss in California,'' \textit{Nature Communications}, vol. 15, no. 1, 2024.

% Fourth citation: b28 (McRoberts 2007) - appears in literature review
\bibitem{b4} R. E. McRoberts and E. O. Tomppo, ``Remote sensing support for national forest inventories,'' \textit{Remote Sensing of Environment}, vol. 110, no. 4, pp. 412--419, 2007.

% Fifth citation: b27 (Liu 2021) - appears in literature review
\bibitem{b5} X. Liu, J. Frey, M. Denter, K. Zielewska-Büttner, N. Still, and B. Koch, ``Mapping standing dead trees in temperate montane forests using a pixel- and object-based image fusion method and stereo WorldView-3 imagery,'' \textit{Ecological Indicators}, vol. 133, 2021.

% Sixth citation: b24 (Briechle 2021) - appears in literature review
\bibitem{b6} S. Briechle, P. Krzystek, and G. Vosselman, ``Silvi-Net -- A dual-CNN approach for combined classification of tree species and standing dead trees from remote sensing data,'' \textit{International Journal of Applied Earth Observation and Geoinformation}, vol. 98, 2021.

% Seventh citation: b23 (Briechle 2020) - appears in literature review
\bibitem{b7} S. Briechle, P. Krzystek, and G. Vosselman, ``Classification of tree species and standing dead trees by fusing UAV-based LiDAR data and multispectral imagery in the 3D deep neural network PointNet,'' \textit{ISPRS Annals of the Photogrammetry, Remote Sensing and Spatial Information Sciences}, vol. V-2-2020, pp. 203--210, 2020.

% Eighth citation: b18 (Ahishali ADA-Net) - appears in methods section
\bibitem{b8} M. Ahishali, A. U. Rahman, E. Heinaro, and S. Junttila, ``ADA-Net: Attention-Guided Domain Adaptation Network with Contrastive Learning for Standing Dead Tree Segmentation Using Aerial Imagery,'' arXiv preprint arXiv:2504.04271, 2025. [Online]. Available: \url{https://arxiv.org/abs/2504.04271}. Accessed: Aug. 8, 2025.

% Ninth citation: b8 (GeeksforGeeks RF) - appears in methods section
\bibitem{b9} ``Random Forest Algorithm in Machine Learning,'' GeeksforGeeks, Jul. 23, 2025. [Online]. Available: \url{https://www.geeksforgeeks.org/machine-learning/random-forest-algorithm-in-machine-learning/}.

% Tenth citation: b9 (Ganie SGD 2023) - appears in methods section
\bibitem{b10} A. G. Ganie and S. Dadvandipour, ``From big data to smart data: a sample gradient descent approach for machine learning,'' \textit{Journal of Big Data}, vol. 10, no. 1, Oct. 2023. doi: \url{https://doi.org/10.1186/s40537-023-00839-9}.

% Eleventh citation: b10 (Awad SVM 2015) - appears in methods section
\bibitem{b11} M. Awad and R. Khanna, ``Support Vector Machines for Classification,'' in \textit{Efficient Learning Machines}, pp. 39--66, 2015. doi: \url{https://doi.org/10.1007/978-1-4302-5990-9_3}.

% Twelfth citation: b11 (Wilimitis 2018) - appears in methods section
\bibitem{b12} D. Wilimitis, ``The Kernel Trick in Support Vector Classification,'' \textit{Medium}, Dec. 12, 2018. [Online]. Available: \url{https://medium.com/data-science/the-kernel-trick-c98cdbcaeb3f}.

% Thirteenth citation: b1 (Ronneberger U-Net 2015) - appears in U-Net section
\bibitem{b13} O. Ronneberger, P. Fischer, and T. Brox, ``U-Net: Convolutional Networks for Biomedical Image Segmentation,'' in \textit{Medical Image Computing and Computer-Assisted Intervention (MICCAI)}, 2015. [Online]. Available: \url{https://lmb.informatik.uni-freiburg.de/people/ronneber/u-net}.

% Fourteenth citation: b4 (NDVI Wikipedia) - appears in U-Net section
\bibitem{b14} ``Normalized Difference Vegetation Index,'' Wikipedia, Wikimedia Foundation. [Online]. Available: \url{https://en.wikipedia.org/wiki/Normalized_difference_vegetation_index}. Accessed: Jun. 22, 2025.

% Fifteenth citation: b3 (NDWI Wikipedia) - appears in U-Net section
\bibitem{b15} ``Normalized Difference Water Index,'' Wikipedia, Wikimedia Foundation. [Online]. Available: \url{https://en.wikipedia.org/wiki/Normalized_difference_water_index}. Accessed: Apr. 7, 2025.

% Sixteenth citation: b19 (Zagoruyko) - appears in U-Net section
\bibitem{b16} S. Zagoruyko, ``pytorchviz -- Visualizing PyTorch Execution Graphs,'' GitHub. [Online]. Available: \url{https://github.com/szagoruyko/pytorchviz}. Accessed: Aug. 9, 2025.

% Seventeenth citation: b16 (Anthropic Claude) - appears in U-Net section
\bibitem{b17} Anthropic, ``Claude,'' 2023. [Online]. Available: \url{https://www.anthropic.com/claude}. Accessed: Aug. 8, 2025.

% Eighteenth citation: b17 (UNSW Katana) - appears in U-Net section
\bibitem{b18} UNSW Sydney Research Technology Services, ``Katana High-Performance Computing Cluster,'' 2025. [Online]. Available: \url{https://docs.restech.unsw.edu.au/index.html}. Accessed: Aug. 8, 2025.

% Nineteenth citation: b21 (Labml.ai) - appears in U-Net discussion section
\bibitem{b19} Labml.ai, ``U-Net: Annotated PyTorch Implementation.'' [Online]. Available: \url{https://nn.labml.ai/unet/index.html}. Accessed: Aug. 9, 2025.

% Twentieth citation: b22 (Qi Snake Conv) - appears in U-Net discussion section
\bibitem{b20} Y. Qi, Y. He, X. Qi, Y. Zhang, and G. Yang, ``Dynamic Snake Convolution Based on Topological Geometric Constraints for Tubular Structure Segmentation,'' arXiv preprint arXiv:2307.08388, Jul. 17, 2023. [Online]. Available: \url{https://arxiv.org/abs/2307.08388}.

\end{thebibliography}